---
title: "day 8 computation"
format: html
editor: visual
---

## Review basics of GGPlot

```{r}
library(tidyverse)
library(here)
library(janitor)
library(patchwork)
library(ggrepel)
library(gghighlight)
library(paletteer)
```

## Read in data

```{r}
lizards<- read_csv(here("data_tidy","lizards.csv"))
```

Do some data wrangling to create a new subset from lizards where you :

1.  Limit the data to only contain western whiptails, colorado checkered, and eastern fence lizards
2.  add a new column with total length converted to cm
3.  group by species and site
4.  return a summary table with mean total length and the standard devation of total length by species and site

```{r}
lizards_subset <- lizards %>% filter(common_name %in% c("western whiptail","colorado checkered","eastern fence")) %>% mutate(length_cm = total_length/10) %>% group_by(common_name, site) %>% summarize(mean = mean(total_length),
                            stand_Dev= sd(total_length))

```

```{r}
ggplot(data = lizards, aes(x = total_length, 
                           y = weight, 
                           color = weight))+ 
  geom_point()+
  scale_y_continuous(limits = c(0,100),
                     breaks = seq(0,100,20),
                     expand = c(0,0))+
  scale_color_gradient(low = "red", high = "navy")


#scale_colorgradientn(colors = c("yellow,"green","blue",...))
```

\

```{r}
ggplot(data = lizards, aes(x = total_length, 
                           y = weight, 
                           color = common_name))+ 
  geom_point()+
  facet_wrap(~common_name, scales = "free")
```

```{r}
# Use dplyr::count to find the total number of lizards by common name in the lizards dataset

lizard_count<- lizards %>%  group_by(common_name) %>% count()
```

```{r}
 ggplot(lizard_count,aes(y= fct_reorder(common_name,n), x = n))+
   geom_col()+
   scale
```
